Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-20 WSSSPE3/report/WSSSPE3_review.tex
Keynote: intro.
Keynote: intro revised.

>>>>

A highlight of WSSSPE3 was the keynote speech delivered by Professor Matthew
Turk from the Department of Astronomy, University of Illinois on ``\emph{Why
Sustain Scientific Software?}''. Turk is a prolific practioner of scientific
software and has extensive experiences working on large collaborative projects
employing modern computing tools. He is also a co-organizer and champion of all
the WSSSPE conferences so far.
